Using Distributed Information Stores for Patient-Clinician Health Data Sharing

### 2013-01-16 patient-clinician-workshop/pccworkshop.tex

\section{Storing and Representing Activity Diaries}
Currently, these devices are designed to upload measurements only to separate, dedicated web sites set up by their manufacturer.  Such sites are poorly suited for the long-term storage of people's activity data for several reasons.  First, none of the sites providelong-term retention or access guarantees of user data (nor HIPAA security guarantees!).  Second, it is difficult for a user to gain a unified understanding of their activity through the disparate interfaces provided, in part due of the widely different visual and interface representations. Finally, many of interfaces represent activity in arbitrary, ``user-friendly'' units, such as ``Sleep score'', ``Fuel'', ``Zen level'' etc., which are difficult or impossible for users to compare.

However, most of these sites have APIs providing programmatic access to raw sensor data.  Our approach has been to leverage such APIs to retrieve a patient's information from all their devices, consolidating it into a uniform, common taxonomy and description logic, like those provided by SNOMED-CT~\cite{stearns2001snomed} and ICD-10~\cite{world1993icd}.  A uniform representation enables such data to be interpretabled and used directly by future clinical medical systems, such as primary care information management systems.

>>>>

\section{Storing and Representing Activity Diaries}
Currently, these devices are designed to upload measurements only to separate, dedicated web sites run by their manufacturers.  Such sites are poorly suited for the long-term storage of people's activity data for several reasons.  First, none of the sites providelong-term retention or access guarantees of user data (nor HIPAA security guarantees!).  Second, it is difficult for a user to gain a unified understanding of their activity through the disparate interfaces provided, in part due of the widely different visual and interface representations. Finally, many of interfaces represent activity in arbitrary, ``user-friendly'' units, such as ``Sleep score'', ``Fuel'', ``Zen level'' etc., which are difficult or impossible for users to compare.

However, most of these sites have APIs providing programmatic access to raw sensor data.  Our approach has been to leverage such APIs to retrieve a patient's information from all their devices, consolidating it into a uniform, common taxonomy and description logic, like those provided by SNOMED-CT \cite{stearns2001snomed} and ICD-10 \cite{world1993icd}.  The goal of such a formalisation is to provide a standard descriptive mechanism by which this data could be interpreted, such as by future clinical medical systems.
